---
title: "Test Notes: Learning RMarkdown for the First Time"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

R Markdown is a great way to write notes or reports on what you're working on in R in a clean and easy to read formating. Best of all, it is all customizable by you!


When you're finished, use **Cmd + Shift + K** (MAC) or **Knit** to save and generate a preview of your notes in a HTML, PDF, or MS word format before exporting. Knit is also good for checking how your work is looking while you're in the process of coding if you're a perfectionist like me.

Alternatively, you can render a html preview that will be sent to your work depository by entering the following command into the console:

```
library(rmarkdown)
render("test 2.Rmd")
```

# Formatting Basics and Writing Down Code

- Single asteriks for *italics* and double asteriks to **bold** words
- Hashtags to create #headers
- Brackets "[ ]" to insert links followed the link entered into into parentheses like so:
```
[google](www.google.com)
```
- " ``` " or **Ctrl + Option + I** (MAC) to create code blocks like above.

These blocks can be use to write down code or can be used to embed code into RMarkdown that can be run and generate previews of datasets, plots, and so forth for our notes and reports. Once you have typed out your code, you can test run the dataset in R by pressing the **green arrow** on the far right side of the block. 

For example, if we wanted to see what the cars dataset within R contained...
```{r cars}
summary(cars)
```

To further customization **Knitr Options** click on the gear on the far right. Alternatively you can embed the customizations within the code itself using a few commands:

```{knitr option commands and explanations}
include = FALSE
prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks.

echo = FALSE
prevents code, but not the results from appearing in the finished file. This is a useful way to embed figures.

message = FALSE
prevents messages that are generated by code from appearing in the finished file.

warning = FALSE
prevents warnings that are generated by code from appearing in the finished.

fig.cap = "..." 
adds a caption to graphical results.

```


## Adding Plots

You can also embed plots, for example:
```{r pressure, echo=FALSE}
plot(pressure)
```
